Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-15 journal paper/content/conclusion.tex
tweaks to final sentence

There are several interesting directions to explore for future work. The model we consider in this paper is well-suited as a model for competition between ad-supported platforms who compete primarily on quality and whose services are provided without cost to users. However, it would be interesting to consider the role that giving the firms to ability to set prices would play as this could potentially enable the firms to compensate users in the earlier periods while it is engaging in exploration and prevent such ``death spiral" effects. The second interesting extension would be to consider a setting with horizontally differentiated user preferences\footnote{This would be similar to the extension in Section \ref{sec:theory-extensions} that considers contextual bandits, though it would be interesting to study how this would change based on different user models that had context-specific user decision rules.} as such a model would be better suited for understanding how competition may induce firms to specialize. In general, there are many further directions to undertake in order to better understand how the intertwined relationship between competition and data generation can help us better understand the digital economy.

>>>>

There are several interesting directions to explore for future work. The model we consider in this paper is well-suited as a model for competition between ad-supported platforms who compete primarily on quality and whose services are provided without cost to users. However, it would be interesting to consider the role that giving the firms to ability to set prices would play as this could potentially enable the firms to compensate users in the earlier periods while it is engaging in exploration and prevent such ``death spiral" effects. The second interesting extension would be to consider a setting with horizontally differentiated user preferences\footnote{This would be similar to the extension in Section \ref{sec:theory-extensions} that considers contextual bandits, though it would be interesting to study how this would change based on different user models that had context-specific user decision rules.} as such a model would be better suited for understanding how competition may induce firms to specialize. In general, there are several further directions to undertake in order to better characterize the intertwined relationship between competition and data generation that can help us better understand competition in the digital economy.
